### 2019-07-10 fe_px_paper/fe_body_text.tex
Merged in Stephen's 1st round comments

The next generation of nuclear medicine 
% would appear to be based upon 
is likely to involve the production of novel, emerging radionuclides\,\cite{Qaim201731}. 
% The targeted and personalized nature of therapy and imaging applications using these novel radionuclides  
These make possible an improvement in clinical practice, offering many patients the possibility for better survival rates and quality lives, and informing researchers in their quest to develop new treatments\,\cite{Mulford2005,Muller2014}.
While the chemical and radioactive decay properties of many of these radionuclides are well-established, their broad-scale  clinical applications are reliant upon well-characterized nuclear data to facilitate large-scale   production. 
% 
% 
% 
% The future of nuclear medicine would appear to be the paradigm of personalized medicine --- targeted radionuclide therapy to spare healthy tissue\,\cite{Mulford2005,Qaim201731}, and theranostic medicine, which pairs an imaging isotope with a therapeutic isotope (frequently, of the same element), to provide simultaneous, real-time dose delivery and verification, leading to drastic reductions in prescribed patient dose\,\cite{Muller2014,Bentzen2005,Srivastava2012}. 
% Other variants of theranostic medicine exist, including pre-imaging for treatment planning, or delivery of a single compound with different radioelements for imaging/therapy where the inter-element biodistribution has been validated.  
% Change up the next sentance a bit
% Novel applications are being explored for several radionuclides whose production methodologies are not established, but their production requires accurate, high-fidelity cross section data.
%\,\cite{Qaim201731}. 
% Many of these applications focus on theranostics, the use of chemically identical (or similar) imaging and therapeutic radiopharmaceuticals for treatment of disease. 
One particular group of  emerging radionuclides are 
% the various 
positron-emitting isotopes of manganese, which have been identified as having potential for a range of diagnostic applications\,\cite{J.2013,Graves2015,Lewis2015,PhysRevC.96.014613,Wooten2017,Hernandez2017}.
In particular, a significant interest has been expressed in producing the emerging radionuclides \ce{^{51}Mn} for clinical use in metabolic PET studies, as well as  \ce{^{52g}Mn} for pre-clinical imaging of neural and immune processes via PET\,\cite{Graves2016}.

However, the modeling of nuclear reactions in this mass region presents numerous challenges including uncertainties in nuclear level densities as a function of spin due to the opening of the $f_{7/2}$ orbital and the presence of enhanced $\gamma$-strength at low energies\,\cite{Voinov2004a,Algin2008,Algin2007}.  
% As 
Therefore, as part of a larger campaign to address deficiencies in cross-cutting nuclear data needs, our group has performed a   measurement of the   nuclear excitation functions of the radionuclides \ce{^{51}Mn},   \ce{^{52m}Mn}, and \ce{^{52g}Mn}.
This was carried out 
% in a
using the thin-foil stacked-target technique to study proton-induced reactions on 
% experiment, using proton irradiation of 
natural iron foils with titanium and copper monitor foils.
% While recent work has been performed in the 40--100\,MeV energy region, t
This work seeks to complement 
% these measurements 
earlier measurements at 40--100\,MeV proton beam energies and extend them down to reaction thresholds, in order to investigate the feasibility of production using the international network   of low-energy medical cyclotrons\,\cite{Graves2016}. 
Furthermore, we are able to use a portion of the data we measured to gain insight into the role of angular momentum in the transitional energy region between compound and direct reactions since both the ground and long-lived isomeric states in \ce{^{52}Mn} were populated.

Manganese radionuclides are desirable for radiopharmaceutical applications, as 
% manganese is a 
the element is chemically versatile,  biologically relevant, and essential in trace quantities. 
Manganese possesses well-established biochemistry, and has been proven to be chelated well by the complexing agent DOTA for tracking monoclonal antibodies, with high biostability at neutral pH\,\cite{Graves2015}.
\ce{^{52}Mn} ($t_{1/2}$ = 5.591$\pm$0.003\,d, $I_{\beta^+}$ = 29.4\%, $E_{\beta\text{, avg}}$ = 0.242\,MeV) has been shown to be useful for immunoPET applications, with its rapid blood clearance offering the possibility for imaging within minutes of injection,
% \,\cite{Dong2015}.
% Its lifetime facilitates regional production and  allows for immunoPET imaging up to 2--3 weeks after administration, giving \ce{^{52}Mn} a longer duration for useful 
making it more useful for imaging  than the more established immunoPET agents \ce{^{89}Zr} or   \ce{^{64}Cu}, and highly suitable for pre-clinical imaging\,\cite{Dong2015}.  
Furthermore, \ce{^{52}Mn}  has high uptake in the heart, liver, kidneys, and pancreas, making it a useful diagnostic agent for pancreatic $\beta$-cell, insulinoma, and porphysome imaging\,\cite{Graves2015}. 
However, its  long half-life and unfavorable high-energy decay gamma-rays 
% (notably, its  744.233\,keV [$I_\gamma = 90.0\,\pm\,1.2\%$], 935.544\,keV [$I_\gamma = 94.5\,\pm\,1.3\%$], and 1434.092\,keV [$I_\gamma = 100.0 \pm 1.4\%$] lines) 
make it undesirable for clinical applications.
% , but easily shipped worldwide and highly suitable for pre-clinical imaging\,\cite{Dong2015}.
The short half-life of the  \ce{^{52m}Mn} isomer ($t_{1/2}$ = 21.1$\pm$0.2\,min)
% , $I_{\beta^+}$\,=\,96.6\%, $E_{\beta\text{,avg}}$ = 1.172\,MeV) offers a much stronger positron emission branch than \ce{^{52g}Mn}, but its short lifetime 
makes production and handling difficult, and its  high-intensity gamma emission (1434.06\,keV [$I_\gamma = 98.2\,\pm\,0.5\%$]) contributes significantly to patient dose\,\cite{Dong2015}.
% Another emerging manganese radionuclide is 
In contrast, \ce{^{51}Mn} ($t_{1/2}$ = 46.2$\pm$0.1\,min, $I_{\beta^+}$ = 96.86\%, $E_{\beta\text{, avg}}$ = 0.964\,MeV), 
% whose short lifetime makes it 
is more clinically suitable for rapid metabolic studies\,\cite{Wang2017}.
% \ce{^{51}Mn} has a comparable positron branch and energy to \ce{^{52m}Mn} and is more suitable for clinical use than the soft positron emissions of \ce{^{52g}Mn}. 
% In addition, 
\ce{^{51}Mn} lacks any strong decay gamma-rays (its longer-lived daughter \ce{^{51}Cr} [$t_{1/2}$ = 27.704$\pm$0.003\,d] has only a single  320.0284\,keV [$I_\gamma = 9.910\,\pm\,0.010\%$] line), making it the best choice of these radionuclides for clinical imaging,\cite{Wang2017}.

@@

% Following  acquisition, the decaying product nuclei corresponding to each observed peak in the collected spectra were identified.
The net  counts in each fitted gamma-ray photopeak were converted into  activities for the decaying  activation products.
% , using calibrated detector efficiencies and gamma-ray intensities for each transition.
% and  corrections for gamma-ray attenuation within each foil packet
% The calibrated detector efficiencies, along with gamma-ray intensities for each transition and  corrections for gamma-ray attenuation within each foil packet, were used to convert the net  counts in each fitted gamma-ray photopeak into an activity for the decay of the activation products.  
% 
% Re-introduce this next line for the journal version
% 
% 
% The nuclear decay data used in this work is tabulated, for reference, in \autoref{tab:fe_nudat_table_monitors} and \autoref{tab:fe_nudat_table_nb} of Appendix \ref{sec:fe_data}.
The   half-lives and gamma-ray branching ratios  used for all calculations of measured cross sections reported in this work  have been taken from the most recent edition of  Nuclear Data Sheets for each  mass chain
\cite{Singh2015a,Chen2011a,Wu2000,Burrows2007,Burrows2006,Burrows2008,Wang2017,Dong2015,Dong2014,JUNDE2008787,Junde2011,Bhat1998,Nesaraja2010,Browne2013,Zuber20151,NICHOLS2012973,ERJUN2001,Singh2007}.
Corrections for gamma-ray attenuation within each foil packet were made, using  photon attenuation coefficients from the XCOM photon cross sections database\,\cite{berger2011xcom}.
% As nearly all of the product nuclei have multiple high-intensity gamma-rays, decay gamma-rays from the product nuclei were measured at multiple points in time (up to 2 weeks after EoB), as well as multiple independent activity measurements at each time point, based on each of its observed gamma-rays.
% Decay gamma-rays from the product nuclei were measured at multiple points in time (up to 2 weeks after EoB), and as nearly all of the product nuclei have multiple high-intensity gamma-rays, this provided independent activity measurements at each time point.
% activity for each gamma-ray possesses a 
The total propagated uncertainty in  activity is the quadrature sum of the uncertainty in  fitted peak areas, uncertainty in detector efficiency calibration, and uncertainty in the gamma-ray branching ratio data.

@@

        \subfigimg[width=0.485\textwidth]{b)}{./figures/after_minimization_plot_alt.pdf}{50}
         %         \refstepcounter{subfigure}
         \label{fig:fe_after_minimization}
   \hspace{-5pt}}%
    \caption{Results of variance minimization through enhancement of the effective areal density of the  aluminum degraders by 4.43\% (55\,MeV stack) and Kapton tape by 5.69\% (25\,MeV stack). A noticeable reduction of variance in measured proton fluence is seen,  particularly at the  rear stack positions.} 
     \label{fig:fe_variance_mins}
\end{figure*}

@@

After irradiation, all foils were confirmed to still be sealed inside their Kapton packets, verifying that no activation products were lost due to packet failure and dispersal.
With the exception of a single foil (Cu-20, in the 25\,MeV stack), each activated foil had a small \enquote{blister} under the Kapton tape layer, caused by a combination of thermal swelling and the formation of short-lived beta activities.
% \comment{Maybe some Ne formed by Al(p,2a)Ne / Si(p,2ap)Ne?}
This blister   verifies that the primary proton beam was incident upon the foil, and provides additional 
% the first 
evidence 
% (before gamma-ray spectrometry) 
that the beam was stopped in the stack between Ti-20 and Cu-20.
% , producing a Bragg peak at this location.  
Using the \ce{^{nat}Ti}(p,x)\ce{^{46}Sc}, \ce{^{nat}Ti}(p,x)\ce{^{48}V}, \ce{^{nat}Cu}(p,x)\ce{^{62}Zn}, and \ce{^{nat}Cu}(p,x)\ce{^{63}Zn} monitor reactions, as discussed in \autoref{sec:proton_transport_fe}, a fluence of 18.8$\pm$1.0\,nAh was calculated to be incident upon the 55\,MeV target stack using the FLUKA fluence model, and a  fluence of 19.0$\pm$1.3\,nAh using the linear fit model.
Similarly, for the 25\,MeV stack, a fluence of 33.2$\pm$4.7\,nAh was calculated to be incident upon the 
% 55\,MeV 
target stack using the FLUKA fluence model, and a  fluence of 37.0$\pm$9.3\,nAh using the linear fit model.
All of these are consistent with the nominal fluence of 20.78\,nAh (for the 55\,MeV stack) and 31.61\,nAh (for the 25\,MeV stack) measured using the 
% beamline 
current integrators.
As fluence loss scales with $\sigma_{\mathrm{tot}}\rho\Delta r$, it is expected that an extrapolation back to the stack entrance (through the SS-3/SS-5 profile monitors) will underestimate the nominal fluence incident upon the box.
This incident fluence dropped by approximately 9.5\% to  17.0$\pm$2.4\,nAh (and by 8.9\% to  17.3$\pm$1.5\,nAh using the linear fit model) over the length of the 55\,MeV stack, which is consistent with similar measurements at the Los Alamos National Laboratory's Isotope Production Facility in the past\,\cite{Voyles2018a,Graves2016}.
This loss of fluence is due to a combination of 
% beam utilization for the various 
(p,x) reactions throughout the target stack, as well as large-angle deflections (primarily in the aluminum degraders) from scattering of the beam.

Using the final proton fluence at each energy position, cross sections for \ce{^{48,49,51}Cr}, \ce{^{48}V},  \ce{^{51,52m,52g,52,54,56}Mn},   \ce{^{52}Fe}, and \ce{^{55,56,57,58m,58g,58}Co}
 were extracted for (p,x) reactions  on \ce{^{nat}Fe} foils up to 55\,MeV, presented in \autoref{tab:fe_rp_table}.
For  (p,x) reactions on \ce{^{nat}Cu}, the (p,x) cross sections for  \ce{^{54}Mn}, \ce{^{57}Ni}, \ce{^{57,60,61}Co},   and \ce{^{60,61,64}Cu}  were extracted, 
% as recorded 
presented in \autoref{tab:cufe_rp_table}.
For  (p,x) reactions on \ce{^{nat}Ti}, the (p,x) cross sections for  \ce{^{43}K} and \ce{^{44g,44m,44,47,48}Sc}  were extracted, 
% as recorded 
presented in \autoref{tab:ti_rp_table}.
In addition, as there exist a number of isomers with radioactive ground states in these mass regions,  independent measurements of isomer-to-ground-state branching ratios for \ce{^{nat}Fe}(p,x)\ce{^{52m/g}Mn}, \ce{^{nat}Fe}(p,x)\ce{^{58m/g}Co}, and \ce{^{nat}Ti}(p,x)\ce{^{44m/g}Sc} were  extracted and are presented in \autoref{tab:fe_ibr_table}.
Comparisons  of the measured cross sections and isomer branching ratios with literature data (retrieved from EXFOR\,\cite{Otuka2014272}) are seen in the figures of Appendices \ref{sec:fe_xs_figures} and \ref{sec:fe_ibr_figures}.
The propagated uncertainty in these cross sections varies widely based on the reaction product in question, with the major components  arising from uncertainty in EoB activity ($\pm$2--10\%), proton fluence ($\pm$5--13\%), and foil areal density ($\pm$0.1--0.3\%).

@@

Several of the activities produced via \ce{^{nat}Fe}(p,x)  could be useful as experimental monitor reactions. 
In particular, \ce{^{nat}Fe}(p,x)\ce{^{56}Co} ($t_{1/2}=77.236\pm0.026$ d, $\epsilon$=100\% to \ce{^{56}Fe}\,\cite{Junde2011})  is a strongly-fed reaction channel (peak cross section of approximately 400\,mb near 12\,MeV), with a sufficiently-long half-life permitting offline gamma spectrometry,  and  cannot be populated via secondary neutrons incident upon the monitor target. 
It possesses a number of intense gamma-rays, which are distinct from those populated by daughter states in the decay of  \ce{^{56}Mn}, and the gammas which are produced both in the decay of  \ce{^{56}Co} and  \ce{^{56}Mn} may be easily resolved based on differences in intensity and half-life. 
Similarly,  \ce{^{nat}Fe}(p,x)\ce{^{54}Mn}  ($t_{1/2}=312.20\pm0.020$ d, $\epsilon$=100\% to \ce{^{54}Cr}\,\cite{Dong2014}) has a convenient half-life and strong cross section (peak of approximately 160\,mb near 40\,MeV), and is immune from two different reactions on the same monitor foil leading to states in the same daughter nuclide.
This reaction could be useful for intermediate- to high-energy protons ($E_p \geq$30\,MeV), but would be susceptible to production via the high-energy secondary neutrons  (threshold 12.1\,MeV off of \ce{^{56}Fe}) produced in these facilities, though (p,x) production rates should dominate (n,x) through both particle flux and cross section.

\textred{All: feel free to add additional details of 51/52Mn production here...}

>>>>

Clinical practice of nuclear medicine is rapidly growing with the inclusion of a broader array of radiopharmaceuticals. 
Future growth is anticipated, given the pre-clinical success of many  new and emerging radionuclides. 
Although the physical and chemical properties of these novel radionuclides tend to be
% The next generation of nuclear medicine 
% % would appear to be based upon 
% is likely to involve the production of novel, emerging radionuclides\,\cite{Qaim201731}. 
% % The targeted and personalized nature of therapy and imaging applications using these novel radionuclides  
% These make possible an improvement in clinical practice, offering many patients the possibility for better survival rates and quality lives, and informing researchers in their quest to develop new treatments\,\cite{Mulford2005,Muller2014}.
% While the chemical and radioactive decay properties of many of these radionuclides are 
well-established, their broad-scale  clinical applications are reliant upon well-characterized nuclear data to facilitate large-scale   production. 
% 
% 
% 
% The future of nuclear medicine would appear to be the paradigm of personalized medicine --- targeted radionuclide therapy to spare healthy tissue\,\cite{Mulford2005,Qaim201731}, and theranostic medicine, which pairs an imaging isotope with a therapeutic isotope (frequently, of the same element), to provide simultaneous, real-time dose delivery and verification, leading to drastic reductions in prescribed patient dose\,\cite{Muller2014,Bentzen2005,Srivastava2012}. 
% Other variants of theranostic medicine exist, including pre-imaging for treatment planning, or delivery of a single compound with different radioelements for imaging/therapy where the inter-element biodistribution has been validated.  
% Change up the next sentance a bit
% Novel applications are being explored for several radionuclides whose production methodologies are not established, but their production requires accurate, high-fidelity cross section data.
%\,\cite{Qaim201731}. 
% Many of these applications focus on theranostics, the use of chemically identical (or similar) imaging and therapeutic radiopharmaceuticals for treatment of disease. 
One particular set of  emerging radionuclides are 
% the various 
positron-emitting isotopes of manganese, which have been identified as having potential for a range of diagnostic applications\,\cite{J.2013,Graves2015,Lewis2015,PhysRevC.96.014613,Wooten2017,Hernandez2017}.
In particular, a significant interest has been expressed in producing the emerging radionuclides \ce{^{51}Mn} for clinical use in quantitative PET studies, as well as  \ce{^{52g}Mn} for pre-clinical imaging of neural and immune processes via PET\,\cite{Graves2016}.

% However, the m
Modeling of nuclear reactions in 
% this 
the A=40--70 mass region presents numerous challenges including uncertainties in nuclear level densities as a function of spin due to the opening of the $f_{7/2}$ orbital and the presence of enhanced $\gamma$-strength at low energies\,\cite{Voinov2004a,Algin2008,Algin2007}.  
% As 
Therefore, as part of a larger campaign to address deficiencies in cross-cutting nuclear data needs, our group has performed a   measurement of the   nuclear excitation functions of the radionuclides \ce{^{51}Mn},   \ce{^{52m}Mn}, and \ce{^{52g}Mn} from proton-induced reactions on natural iron.
This was carried out 
% in a
using the thin-foil stacked-target technique to study proton-induced reactions on 
% experiment, using proton irradiation of 
natural iron foils with titanium and copper monitor foils.
% While recent work has been performed in the 40--100\,MeV energy region, t
This work 
% seeks to 
complements 
% these measurements 
earlier measurements using 40--100\,MeV protons  and extends them down to reaction thresholds,  to investigate the feasibility of production using the international network   of low-energy medical cyclotrons\,\cite{Graves2016}. 
Furthermore, we are able to use a portion of the data we measured to gain insight into the role of angular momentum in the transitional energy region between compound and direct reactions since both the ground and long-lived isomeric states in \ce{^{52}Mn} were populated.

Manganese radionuclides are desirable for radiopharmaceutical applications, as 
% manganese is a 
the element is chemically versatile,  biologically relevant, and essential in trace quantities. 
Manganese possesses well-established biochemistry, and has been proven to be chelated well by the complexing agent DOTA for tracking monoclonal antibodies, with high biostability at neutral pH\,\cite{Graves2015}.
\ce{^{52}Mn} ($t_{1/2}$ = 5.591$\pm$0.003\,d, $I_{\beta^+}$ = 29.4\%, $E_{\beta\text{, avg}}$ = 0.242\,MeV\,\cite{Dong2015}) has been shown to be useful for immunoPET applications, with its rapid blood clearance offering the possibility for imaging within minutes of injection,
% \,\cite{Dong2015}.
% Its lifetime facilitates regional production and  allows for immunoPET imaging up to 2--3 weeks after administration, giving \ce{^{52}Mn} a longer duration for useful 
making it more useful for imaging  than the more established immunoPET agents \ce{^{89}Zr} or   \ce{^{64}Cu}, and highly suitable for pre-clinical imaging.  
Furthermore, \ce{^{52}Mn}  has high uptake in the heart, liver, kidneys, and pancreas, making it a useful diagnostic agent for pancreatic $\beta$-cell, insulinoma, and porphysome imaging\,\cite{Graves2015}. 
However, its  long half-life and unfavorable high-energy decay gamma-rays 
% (notably, its  744.233\,keV [$I_\gamma = 90.0\,\pm\,1.2\%$], 935.544\,keV [$I_\gamma = 94.5\,\pm\,1.3\%$], and 1434.092\,keV [$I_\gamma = 100.0 \pm 1.4\%$] lines) 
make it undesirable for clinical applications.
% , but easily shipped worldwide and highly suitable for pre-clinical imaging\,\cite{Dong2015}.
The short half-life of the  \ce{^{52m}Mn} isomer ($t_{1/2}$ = 21.1$\pm$0.2\,min)
% , $I_{\beta^+}$\,=\,96.6\%, $E_{\beta\text{,avg}}$ = 1.172\,MeV) offers a much stronger positron emission branch than \ce{^{52g}Mn}, but its short lifetime 
makes production and handling difficult, and its  high-intensity gamma emission (1434.06\,keV [$I_\gamma = 98.2\,\pm\,0.5\%$]) contributes significantly to patient dose\,\cite{Dong2015}.
% Another emerging manganese radionuclide is 
In contrast, \ce{^{51}Mn} ($t_{1/2}$ = 46.2$\pm$0.1\,min, $I_{\beta^+}$ = 96.86\%, $E_{\beta\text{, avg}}$ = 0.964\,MeV\,\cite{Wang2017}), 
% whose short lifetime makes it 
is more clinically suitable for rapid metabolic studies.
% \ce{^{51}Mn} has a comparable positron branch and energy to \ce{^{52m}Mn} and is more suitable for clinical use than the soft positron emissions of \ce{^{52g}Mn}. 
% In addition, 
\ce{^{51}Mn} lacks any strong decay gamma-rays (its longer-lived daughter \ce{^{51}Cr} [$t_{1/2}$ = 27.704$\pm$0.003\,d] has only a single  320.0284\,keV [$I_\gamma = 9.910\,\pm\,0.010\%$] line), making it the best choice of these radionuclides for clinical imaging.
% ,\cite{Wang2017}.

@@

% Following  acquisition, the decaying product nuclei corresponding to each observed peak in the collected spectra were identified.
The net  counts in each fitted gamma-ray photopeak were converted into  activities for the decaying  activation products.
% , using calibrated detector efficiencies and gamma-ray intensities for each transition.
% and  corrections for gamma-ray attenuation within each foil packet
% The calibrated detector efficiencies, along with gamma-ray intensities for each transition and  corrections for gamma-ray attenuation within each foil packet, were used to convert the net  counts in each fitted gamma-ray photopeak into an activity for the decay of the activation products.  
% 
% Re-introduce this next line for the journal version
% 
% 
% The nuclear decay data used in this work is tabulated, for reference, in \autoref{tab:fe_nudat_table_monitors} and \autoref{tab:fe_nudat_table_nb} of Appendix \ref{sec:fe_data}.
The   half-lives and gamma-ray branching ratios  used for all calculations of measured cross sections reported in this work  have been taken from the most recent edition of  Nuclear Data Sheets for each  mass chain
\cite{Singh2015a,Chen2011a,Wu2000,Burrows2007,Burrows2006,Burrows2008,Wang2017,Dong2015,Dong2014,JUNDE2008787,Junde2011,Bhat1998,Nesaraja2010,Browne2013,Zuber20151,NICHOLS2012973,ERJUN2001,Singh2007}.
Corrections for gamma-ray attenuation within each foil packet were made, using  photon attenuation coefficients from the XCOM photon cross sections database\,\cite{berger2011xcom}.
% As nearly all of the product nuclei have multiple high-intensity gamma-rays, decay gamma-rays from the product nuclei were measured at multiple points in time (up to 2 weeks after EoB), as well as multiple independent activity measurements at each time point, based on each of its observed gamma-rays.
% Decay gamma-rays from the product nuclei were measured at multiple points in time (up to 2 weeks after EoB), and as nearly all of the product nuclei have multiple high-intensity gamma-rays, this provided independent activity measurements at each time point.
% activity for each gamma-ray possesses a 
EoB activities were determined by $\chi^2$-fitting of all observed decay gammas for a product to the decay curve.
The total  uncertainty in  activity is the propagated sum of the uncertainty in  fitted peak areas, uncertainty in detector efficiency calibration,  uncertainty in the gamma-ray branching ratio data, and uncertainty in photon attenuation coefficients (taken as~5\%).

@@

        \subfigimg[width=0.485\textwidth]{b)}{./figures/after_minimization_plot_alt.pdf}{50}
         %         \refstepcounter{subfigure}
         \label{fig:fe_after_minimization}
   \hspace{-5pt}}%
    \caption{Results of variance minimization through increasing the effective areal density of the  aluminum degraders by 4.43\% (55\,MeV stack) and Kapton tape by 5.69\% (25\,MeV stack). A noticeable reduction of variance in measured proton fluence is seen,  particularly at the  rear stack positions.} 
     \label{fig:fe_variance_mins}
\end{figure*}

@@

After irradiation, all foils were confirmed to still be sealed inside their Kapton packets, verifying that no activation products were lost due to packet failure and dispersal.
With the exception of a single foil (Cu-20, in the 25\,MeV stack), each activated foil had a small \enquote{blister} under the Kapton tape layer, caused by a combination of thermal swelling, off-gassing of oxides, and the formation of gaseous short-lived beta activities in the tape.
% \comment{Maybe some Ne formed by Al(p,2a)Ne / Si(p,2ap)Ne?}
This blister   verifies that the primary proton beam was incident upon the foil, and provides additional 
% the first 
evidence 
% (before gamma-ray spectrometry) 
that the beam was stopped in the stack between Ti-20 and Cu-20.
% , producing a Bragg peak at this location.  
Using the \ce{^{nat}Ti}(p,x)\ce{^{46}Sc}, \ce{^{nat}Ti}(p,x)\ce{^{48}V}, \ce{^{nat}Cu}(p,x)\ce{^{62}Zn}, and \ce{^{nat}Cu}(p,x)\ce{^{63}Zn} monitor reactions, as discussed in \autoref{sec:proton_transport_fe}, a fluence of 18.8$\pm$1.0\,nAh was calculated to be incident upon the 55\,MeV target stack using the FLUKA fluence model, and a  fluence of 19.0$\pm$1.3\,nAh using the linear fit model.
Similarly, for the 25\,MeV stack, a fluence of 33.2$\pm$4.7\,nAh was calculated to be incident upon the 
% 55\,MeV 
target stack using the FLUKA fluence model, and a  fluence of 37.0$\pm$9.3\,nAh using the linear fit model.
All of these are consistent with the nominal fluence of 20.78\,nAh (for the 55\,MeV stack) and 31.61\,nAh (for the 25\,MeV stack) measured using the 
% beamline 
current integrators.
As fluence loss scales with $\sigma_{\mathrm{tot}}\rho\Delta r$, it is expected that an extrapolation back to the stack entrance (through the SS-3/SS-5 profile monitors) will underestimate the nominal fluence incident upon the box.
This incident fluence dropped by approximately 9.5\% to  17.0$\pm$2.4\,nAh (and by 8.9\% to  17.3$\pm$1.5\,nAh using the linear fit model) over the length of the 55\,MeV stack, which is consistent with similar measurements at the Los Alamos National Laboratory's Isotope Production Facility in the past\,\cite{Voyles2018a,Graves2016}.
This loss of fluence is due to a combination of 
% beam utilization for the various 
(p,x) reactions throughout the target stack, as well as large-angle deflections (primarily in the aluminum degraders) from scattering of the beam.

Using the final proton fluence at each energy position, cross sections for \ce{^{48,49,51}Cr}, \ce{^{48}V},  \ce{^{51,52m,52g,52,54,56}Mn},   \ce{^{52}Fe}, and \ce{^{55,56,57,58m,58g,58}Co}
 were extracted for (p,x) reactions  on \ce{^{nat}Fe} foils up to 55\,MeV, presented in \autoref{tab:fe_rp_table}.
For  (p,x) reactions on \ce{^{nat}Cu}, the (p,x) cross sections for  \ce{^{54}Mn}, \ce{^{57}Ni}, \ce{^{57,60,61}Co},   and \ce{^{60,61,64}Cu}  were extracted, 
% as recorded 
presented in \autoref{tab:cufe_rp_table}.
For  (p,x) reactions on \ce{^{nat}Ti}, the (p,x) cross sections for  \ce{^{43}K} and \ce{^{44g,44m,44,47,48}Sc}  were extracted, 
% as recorded 
presented in \autoref{tab:ti_rp_table}.
In addition, as there exist a number of isomers with radioactive ground states in these mass regions,  independent measurements of isomer-to-ground-state branching ratios for \ce{^{nat}Fe}(p,x)\ce{^{52m/g}Mn}, \ce{^{nat}Fe}(p,x)\ce{^{58m/g}Co}, and \ce{^{nat}Ti}(p,x)\ce{^{44m/g}Sc} were  extracted and are presented in \autoref{tab:fe_ibr_table}.
Comparisons  of the measured cross sections and isomer branching ratios with literature data (retrieved from EXFOR\,\cite{Otuka2014272}) are seen in the figures of Appendices \ref{sec:fe_xs_figures} and \ref{sec:fe_ibr_figures}.
The propagated uncertainty in these cross sections varies widely based on the reaction product in question, with the major components  arising from uncertainty in EoB activity ($\pm$3--10\%), proton fluence ($\pm$5--13\%), and foil areal density ($\pm$0.1--0.3\%).

@@

Several of the activities produced via \ce{^{nat}Fe}(p,x)  could be useful as experimental monitor reactions. 
In particular, \ce{^{nat}Fe}(p,x)\ce{^{56}Co} ($t_{1/2}=77.236\pm0.026$ d, $\epsilon$=100\% to \ce{^{56}Fe}\,\cite{Junde2011})  is a strongly-fed reaction channel (peak cross section of approximately 400\,mb near 12\,MeV), with a sufficiently-long half-life permitting offline gamma spectrometry,  and  cannot be populated via secondary neutrons incident upon the monitor target. 
It possesses a number of intense gamma-rays, which are distinct from those populated by daughter states in the decay of  \ce{^{56}Mn}, and the gammas which are produced both in the decay of  \ce{^{56}Co} and  \ce{^{56}Mn} may be easily resolved based on differences in intensity and half-life. 
Similarly,  \ce{^{nat}Fe}(p,x)\ce{^{54}Mn}  ($t_{1/2}=312.20\pm0.020$ d, $\epsilon$=100\% to \ce{^{54}Cr}\,\cite{Dong2014}) has a convenient half-life and strong cross section (peak of approximately 160\,mb near 40\,MeV), and is immune from two different reactions on the same monitor foil leading to states in the same daughter nuclide.
This reaction could be useful for intermediate- to high-energy protons ($E_p \geq$30\,MeV), but would be susceptible to production via the high-energy secondary neutrons  (threshold 12.1\,MeV off of \ce{^{56}Fe}) produced in these facilities, though (p,x) production rates should dominate (n,x) through both particle flux and cross section. 
Additionally, the \ce{^{nat}Fe}(p,x)\ce{^{54}Mn} and \ce{^{nat}Fe}(p,x)\ce{^{56}Co} channels have a difference in apparent energetic thresholds of nearly 20\,MeV.
This provides some energy discrimination sensitivity in the same iron foil, particularly in the 20--50\,MeV region, which could be useful for determining incident proton energy near 40\,MeV, where fast neutrons are less significant than deeper in the stack.

% \textred{All: feel free to add additional details of 51/52Mn production here...}
